SunPy - Python for Solar Physics

### 2014-01-28 authors.tex

\author{
% People who have directly contributed to the text, still in no order.
Stuart J Mumford$^1$,
Steven Christe$^2$,
David P\'erez-Su\'arez$^3$,
Andrew R Inglis$^{2,5}$,
Jack Ireland$^{6,2}$,
Albert Y Shih$^2$,
Simon Liedtke$^11$,
Russell J Hewett$^8$, %88
% Contributors to SunPy Sorted thus:
% No. Commits to main repo + commits in open PR's
% Date of most recent contribution
F Mayer$^{12}$, %721
K Hughitt, %446
Nabil Freij$^1$, %52
M Earnshaw, %52
Tomas Meszaros$^{10}$, %17
N Chorley, %17
Samuel M Bennett$^1$, %14
M Malocha, %10
J Evans, %10
A Maverick, %8
M Bates, %6
Andrew J Leonard$^7$, %3
J Ballew, %3
Thomas P Robitaille, %2
B Mampaey, %2
%Hypnus1803 %1
and 
A Kustov %1
}

>>>>

\author{
% People who have directly contributed to the text, still in no order.
Stuart J Mumford$^1$,
Steven Christe$^2$,
David P\'erez-Su\'arez$^3$,
Andrew R Inglis$^{2,5}$,
Jack Ireland$^{6,2}$,
Albert Y Shih$^2$,
Simon Liedtke$^{11}$,
Russell J Hewett$^8$, %88
% Contributors to SunPy Sorted thus:
% No. Commits to main repo + commits in open PR's
% Date of most recent contribution
F Mayer$^{12}$, %721
K Hughitt, %446
Nabil Freij$^1$, %52
M Earnshaw, %52
Tomas Meszaros$^{10}$, %17
N Chorley, %17
Samuel M Bennett$^1$, %14
M Malocha, %10
J Evans, %10
A Maverick, %8
M Bates, %6
Andrew J Leonard$^7$, %3
J Ballew, %3
Thomas P Robitaille, %2
B Mampaey, %2
%Hypnus1803 %1
and 
A Kustov %1
}
